### 2024-10-23 Scripts/Manuscript/manuscript.Rmd
additional clean-up before pre-print

## Credibility & Measurement
Psychological constructs, such as affective states or intelligence, cannot be measured directly. Psychological measurements involve random measurement errors and uncertainties about whether the targeted construct is indeed well reflected in the scores retrieved from the measurement procedure.

@@

This manuscript was created in RStudio [*v`r rstudioapi::versionInfo()$version`*\; @R-Rstudio] with R Version `r paste0(R.Version()$major, ".", R.Version()$minor)` [@R-base], and generated using the Workflow for Open Reproducible Code in Science [*v`r getNamespaceVersion("worcs")[[1]]`*\; @vanlissaWORCS2021] to ensure reproducibility and transparency. All code and data used to generate this manuscript and its results are available at: <https://github.com/CasGoos/measurement_and_replication> and <https://osf.io/9r8yt/>.

@@

### Replication Protocols
The replication protocols refer to the publicly available protocols describing the background, methodology, and analysis of each set of replications of a given original study across multiple labs. These were retrieved from the OSF pages of the Many Labs projects (the search strategy and OSF file locations can be found in the [data retrieval information](../../SupplementaryMaterials/data_retrieval_information.Rmd) supplementary document; URL <https://github.com/CasGoos/measurement_and_replication/blob/master/SupplementaryMaterials/data_retrieval_information.Rmd>).

@@

Figure \@ref(fig:ReliabilityReportingFlowDiagram) depicts the flow of measures in relation to reliability reporting. First, it shows that almost half of the measures in both replication (N = `r apa_num(sum(data_h456_replications$N_items == "1 item measure"))`) and original research (N = `r apa_num(sum(data_h456_original$N_items == "1 item measure"))`) were single-item measures. When looking at the multiple-item measures, the graph illustrates that `r N_reported_reliabilities_replications` measures in the replication protocols (`r apa_num((as.numeric(N_reported_reliabilities_replications_number_style) / sum(data_h456_replications$N_items != "1 item measure")) * 100, digits = 1)` \%) and `r N_reported_reliabilities_original` measures in the original articles (`r apa_num((as.numeric(N_reported_reliabilities_original) / sum(data_h456_original$N_items != "1 item measure")) * 100, digits = 1)` \%) reported a reliability coefficient. The most commonly reported reliability coefficient was Cronbach’s Alpha, which accounted for `r apa_num(sum(data_h456_replications$reliability_type == "alpha"), numerals = FALSE)` reported reliabilities in the replication protocols, and `r apa_num(sum(data_h456_original$reliability_type == "alpha"))` in the original articles.

@@

Reliability was more commonly reported in original (N = `r N_reported_reliabilities_original`; `r apa_num((as.numeric(N_reported_reliabilities_original) / nrow(data_h456_original)) * 100, digits = 1)` \%) as compared to replication research (N = `r N_reported_reliabilities_replications_number_style`; `r apa_num((as.numeric(N_reported_reliabilities_replications_number_style) / nrow(data_h456_replications)) * 100, digits = 1)` \%, $\chi^{2}$(`r apa_num(reliability_reporting_test_result$parameter)`) = `r apa_num(reliability_reporting_test_result$statistic)`, *p* = `r apa_p(reliability_reporting_test_result$p.value)`). Validity evidence was similarly reported infrequently. Validity evidence from a factor analysis was reported in `r apa_num(sum(data_h456_original$sel_psychometric_evidence_REV != "None" & data_h456_original$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)"), numerals = FALSE)` original articles, while in only `r apa_num(sum(data_h456_replications$sel_psychometric_evidence_REV != "None" & data_h456_replications$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)"), numerals = FALSE)` replications. This difference was not significant ($\chi^{2}$(`r apa_num(factor_reporting_test_result$parameter)`) = `r apa_num(factor_reporting_test_result$statistic)`, *p* = `r apa_p(factor_reporting_test_result$p.value)`), however the total number of factor analyses reported was low.

To gain a better understanding of the validity of the included measurements, we also conducted pre-registered exploratory analyses testing the unidimensionality of `r nrow(cfa_results)` measures with available replication data using a confirmatory factor analysis. We reasoned that most of the included measures should theoretically tap into a single construct, so evidence for unidimensionality would serve as a proxy for evidence of higher construct validity. We found that `r sum(cfa_results$Single_factor == "Yes", na.rm = TRUE)` of these measures (`r apa_num((sum(cfa_results$Single_factor == "Yes", na.rm = TRUE) / nrow(cfa_results)) * 100, digits = 1)` \%) met our criteria for unidimensionality (see [Supplementary Analyses A](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_pre-reg_analyses.Rmd) for further details).

@@

However, it is worth noting that the spillover effect was only observed for QMPs coded with the revised coding protocol. Neither hypothesis was supported by the data on QMPs obtained with the initial coding protocol (see [Supplementary Analyses D](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_initial_QMP_analyses.Rmd for results based on the initial protocol). Furthermore, these hypotheses were supported by only one of the multilevel models. These were limited in group and sample size however, making their results uncertain.

>>>>

## Credibility & Measurement

Psychological constructs, such as affective states or intelligence, cannot be measured directly. Psychological measurements involve random measurement errors and uncertainties about whether the targeted construct is indeed well reflected in the scores retrieved from the measurement procedure.

@@

This manuscript was created in RStudio [*v`r rstudioapi::versionInfo()$version`*\; @R-Rstudio] with R Version `r paste0(R.Version()$major, ".", R.Version()$minor)` [@R-base], and generated using the Workflow for Open Reproducible Code in Science [*v`r getNamespaceVersion("worcs")[[1]]`*\; @vanlissaWORCS2021] to ensure reproducibility and transparency. All code and data used to generate this manuscript and its results are available at: <https://github.com/CasGoos/measurement_and_replication> and <https://osf.io/9r8yt/> (DOI: 10.17605/OSF.IO/9R8YT).

@@

### Replication Protocols

The replication protocols refer to the publicly available protocols describing the background, methodology, and analysis of each set of replications of a given original study across multiple labs. These were retrieved from the OSF pages of the Many Labs projects (the search strategy and OSF file locations can be found in the [data retrieval information](../../SupplementaryMaterials/data_retrieval_information.Rmd) supplementary document; URL <https://github.com/CasGoos/measurement_and_replication/blob/master/SupplementaryMaterials/data_retrieval_information.Rmd>).

@@

Figure \@ref(fig:ReliabilityReportingFlowDiagram) depicts the flow of measures in relation to reliability reporting. First, it shows that almost half of the measures in both replication (N = `r apa_num(sum(data_h456_replications$N_items == "1 item measure"))`) and original research (N = `r apa_num(sum(data_h456_original$N_items == "1 item measure"))`) were single-item measures. When looking at the multiple-item measures, the graph illustrates that `r N_reported_reliabilities_replications` measures in the replication protocols (`r apa_num((as.numeric(N_reported_reliabilities_replications_number_style) / sum(data_h456_replications$N_items != "1 item measure")) * 100, digits = 1)` %) and `r N_reported_reliabilities_original` measures in the original articles (`r apa_num((as.numeric(N_reported_reliabilities_original) / sum(data_h456_original$N_items != "1 item measure")) * 100, digits = 1)` %) reported a reliability coefficient. The most commonly reported reliability coefficient was Cronbach’s Alpha, which accounted for `r apa_num(sum(data_h456_replications$reliability_type == "alpha"), numerals = FALSE)` reported reliabilities in the replication protocols, and `r apa_num(sum(data_h456_original$reliability_type == "alpha"))` in the original articles.

@@

Reliability was more commonly reported in original (N = `r N_reported_reliabilities_original`; `r apa_num((as.numeric(N_reported_reliabilities_original) / nrow(data_h456_original)) * 100, digits = 1)` %) as compared to replication research (N = `r N_reported_reliabilities_replications_number_style`; `r apa_num((as.numeric(N_reported_reliabilities_replications_number_style) / nrow(data_h456_replications)) * 100, digits = 1)` %, $\chi^{2}$(`r apa_num(reliability_reporting_test_result$parameter)`) = `r apa_num(reliability_reporting_test_result$statistic)`, *p* = `r apa_p(reliability_reporting_test_result$p.value)`). Validity evidence was similarly reported infrequently. Validity evidence from a factor analysis was reported in `r apa_num(sum(data_h456_original$sel_psychometric_evidence_REV != "None" & data_h456_original$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)"), numerals = FALSE)` original articles, while in only `r apa_num(sum(data_h456_replications$sel_psychometric_evidence_REV != "None" & data_h456_replications$sel_psychometric_evidence_REV != "Not Apllicable (only report this if psychometric evidence would not be possible for this measure, otherwise report as None)"), numerals = FALSE)` replications. This difference was not significant ($\chi^{2}$(`r apa_num(factor_reporting_test_result$parameter)`) = `r apa_num(factor_reporting_test_result$statistic)`, *p* = `r apa_p(factor_reporting_test_result$p.value)`), however the total number of factor analyses reported was low.

To gain a better understanding of the validity of the included measurements, we also conducted pre-registered exploratory analyses testing the unidimensionality of `r nrow(cfa_results)` measures with available replication data using a confirmatory factor analysis. We reasoned that most of the included measures should theoretically tap into a single construct, so evidence for unidimensionality would serve as a proxy for evidence of higher construct validity. We found that `r sum(cfa_results$Single_factor == "Yes", na.rm = TRUE)` of these measures (`r apa_num((sum(cfa_results$Single_factor == "Yes", na.rm = TRUE) / nrow(cfa_results)) * 100, digits = 1)` %) met our criteria for unidimensionality (see [Supplementary Analyses A](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_pre-reg_analyses.Rmd) for further details).

@@

However, it is worth noting that the spillover effect was only observed for QMPs coded with the revised coding protocol. Neither hypothesis was supported by the data on QMPs obtained with the initial coding protocol (see [Supplementary Analyses D](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_initial_QMP_analyses.Rmd%20for%20results%20based%20on%20the%20initial%20protocol). Furthermore, these hypotheses were supported by only one of the multilevel models. These were limited in group and sample size however, making their results uncertain.
